---
title: "p8105_hw1_sc5351"
output: github_document
date: "2023.09.23"
---


```{r setup}
library(moderndive)
data("early_january_weather")
```
## Problem 1
## Description of the dataset

#The early_january_weather datasetdescribes the relevant details of the weather changes in January 2013.

variables <- colnames(early_january_weather)

dewpoint <- dewp(early_january_weather)

windspeed <- wind_speed(early_january_weather)

pressure <- presssure(early_january_weather)

## The size of the data
num_rows <- nrow(early_january_weather)

num_cols <- ncol(early_january_weather)

## The mean temperature
mean_temp <- mean(early_january_weather$temp)

## Scatterplot of x and y

```{r}
library(ggplot2)
plot_df = ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
plot_df
```

## Export scatterplot
```{r}
ggsave("scatterplot.pdf", plot_df)
```

## Problem 2

```{r}
library(tidyverse)
# create the data frame
random_numeric <- rnorm(10)
logical_vector <- rnorm(10) > 0
character_vector = c("S","H","A","O","Y","U","C","H","E","N")
factor_levels <- c("Level1", "Level2", "Level3")
my_vector <- sample(factor_levels, 10, replace = TRUE)
factor_vector <- factor(my_vector, levels = factor_levels)

my_data_frame <- data.frame(
  RandomSample = random_numeric,
  LogicalVector = logical_vector,
  CharacterVector = character_vector,
  FactorVector = factor_vector
)
my_data_frame

# calculate the mean variable
mean_random <- mean(pull(my_data_frame, RandomSample))
mean_logical <- mean(pull(my_data_frame, LogicalVector))
mean_character <- mean(pull(my_data_frame, CharacterVector))
mean_factor <- mean(pull(my_data_frame, FactorVector))

mean_random
mean_logical
mean_character
mean_factor

# I found that random sample and logical vector have the value, but character and factor vector don't.

numeric_logical <- as.numeric(my_data_frame$logical_vector)
numeric_character <- as.numeric(my_data_frame$character_vector)
numeric_factor <- as.numeric(my_data_frame$factor_vector)

# random sample and logical vector have the value, but character and factor vector show that NA. and it has already shown the mean variable.
```


